%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{scrlayer-scrpage}
\usepackage{lastpage}

\reversemarginpar % Move the margin to the left of the page 

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document

\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, hidelinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011} % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{0.8em}} % Define a command for descriptions of each entry - change spacing and font sizes here

\usepackage[english]{babel}
\usepackage{iflang}

\newcommand{\ifet}[2]{\IfLanguageName{estonian}{#1}{#2}}

%----------------------------------------------------------------------------------------

\begin{document}

\pagestyle{plain} % Stop the page count at the bottom of the first page
%\KOMAoption{footinclude}{sdfsdfsdf}
\rofoot[\thepage / \pageref{LastPage}]{\thepage}


%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Mart Oruaas}}\vspace{1.5em} % Your name

\noindent\spacedlowsmallcaps{\ifet{Kontaktandmed}{Personal Information}}\vspace{0.5em} % Personal information heading

\NewEntry{}{\ifet{Sündinud 16.novembril 1976}{\textit{Born in Estonia,}{16 November 1976}}} % Birthplace and date

\NewEntry{\ifet{e-post}{e-mail}}{\href{mailto:mart.oruaas@gmail.com}{mart.oruaas@gmail.com}} % Email address

%\NewEntry{website}{\href{http://www.johnsmith.com}{http://www.johnsmith.com}} % Personal website

\NewEntry{\ifet{telefon}{phone}}{(M) +372 5100227} % \ \ $\cdotp$\ \ (M) +1 (000) 111 1112} % Phone number(s)

\vspace{1em} % Extra white space between the personal information section and goal

%\noindent\spacedlowsmallcaps{Goal}\vspace{1em} % Goal heading, could be used for a quotation or short profile instead

%\Description{Gain fundamental experience in my area of interest and expertise.}\vspace{2em} % Goal text

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{\ifet{Haridus}{Education}}\vspace{1em}

\NewEntry{1995-2001}{\ifet{Tallinna Tehnikaülikool}{Tallinn Technical University}}

\Description{\MarginText{\ifet{Tehnikateaduste bakalaureus}{Bachelor of Science}} \ifet{Informaatika}{Informatics}\newline 
}

%------------------------------------------------

%\NewEntry{2007-2010}{The University of California, Berkeley}

%\Description{\MarginText{Bachelor of Business Studies}GPA: 7.5\ \ $\cdotp$\ \ \textit{Commerce Specialization}\ \ $\cdotp$\ \ School: Business and Administration\newline
%Description: This degree focussed heavily on important things such as personnel management and mundane paperwork.}

%------------------------------------------------

\vspace{1em} % Extra space between major sections


%----------------------------------------------------------------------------------------

%\noindent\spacedlowsmallcaps{Professional skills}\vspace{1em}


%\small{1231313}
%\NewEntry{}{}{asfdfdsgsdfgdfg}

%\NewEntry{1995-2001}{Tallinn Technical University}

%\Description{\MarginText{Bachelor of Science} Informatics\newline 
%}

%------------------------------------------------

%\NewEntry{2007-2010}{The University of California, Berkeley}

%\Description{\MarginText{Bachelor of Business Studies}GPA: 7.5\ \ $\cdotp$\ \ \textit{Commerce Specialization}\ \ $\cdotp$\ \ School: Business and Administration\newline
%Description: This degree focussed heavily on important things such as personnel management and mundane paperwork.}

%------------------------------------------------


%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{\ifet{Erialased oskused}{Professional Skills}}\vspace{1em}

\newcommand{\skills}[4]{\Description{\MarginText{\ifet{#1}{#3}}\ifet{#2}{#4}}}

\skills{Hajussüsteemid}{Protokollide disain, hajussüsteemide töökindlus, jõudlus ja turvalisus. Süsteemide formaalne spetsifitseerimine ja verifitseerimine.}{Distributed systems}{Protocol design, reliability, performance and security of distributed systems. Formal specification and verification of distributed software systems.}

\skills{Andmeturve}{Infosüsteemide formaalne turvaanalüüs. Turvaprotokollide disain ja realiseerimine. Tarkvaratehniliste meetmete rakendamine tarkvara ründekindluste tõstmiseks.}{Information security}{Formal security analysis of information systems. Design and implementation of security protocols. Software hardening through advanced methods in software engineering.}

\skills{Programmeerimiskeeled}{C, C++, Java, Scala, Ruby, Python, Rust, Go, SQL, JavaScript.}{Programming languages}{C, C++, Java, Scala, Ruby, Python, Rust, Go, SQL, JavaScript.}

\vspace{1em} % Extra space between major sections

\skills{Formaalsed spetsifitseerimiskeeled}{TLA+/PlusCal, Coq, Tamarin, ProVerif.}{Formal specification languages}{TLA+/PlusCal, Coq, Tamarin, ProVerif.}


%------------------------------------------------

\vspace{2.0em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\newcommand{\competencies}[2]{\ifet{Kompetents}{Competencies}: \textit{\ifet{#1}{#2}}}

\noindent\spacedlowsmallcaps{\ifet{T{\"o}{\"o}kogemus}{Work Experience}}\vspace{1em}

%------------------------------------------------

\NewEntry{2014--Present}{\ifet{Süsteemiarhitekt}{System Architect}, \textsc{Cybernetica AS}  --- Tallinn}

\Description{\MarginText{Cybernetica AS}\ifet{Mitmesugused andmeturbe-alased arendusprojektid. Krüptograafiliste protokollide disain ja realiseerimine. Infosüsteemide turvaanalüüs. Rakendusuuringud krüptograafia ja infoturbe valdkonnast.}{Working on information security related software projects. Krüptograafiliste protokollide}\newline
	\competencies{C++, Java, Python, hajussüsteemide arendus}{C++, Java, Python, distributed and concurrent programming, algorithm and protocol design. Cryptographic protocol design and implementation. Formal security analysis of information systems. Applied research in the fields of cryptography and information security.}
	
}

\NewEntry{2013--2014}{\ifet{Vabakutseline tarkvaraarendaja}{Freelance software engineer}}

\Description{\MarginText{}\ifet{Spetsiifilised allhanketööd mitmele startup-firmale.}{Worked as software developer for several early-stage startups.}\newline
	\competencies{C++, Python, algoritmide disain}{C++, Python, algorithm design}
}

%------------------------------------------------

\NewEntry{2012--2013}{\ifet{Tarkvaraarhitekt}{Software Architect}, \textsc{GrabCAD}  --- Tallinn}

\Description{\MarginText{GrabCAD}\ifet{Tarkvaraarhitekt GrabCADi Tallinna arenduskontoris. Vastutav grabcad.com teenusserverite tarkvaraarhitektuuri, skaleeruvuse ja turvalisuse eest.}{Software Architect in GrabCAD Tallinn development office. Responsible for structuring, scaling and securing GrabCAD backend services.}\newline
	\competencies{Veebiteenuste arendus, skaleerimine ja turvalisus. Mastaapsete rakenduste haldamine pilveteenuse pakkuja keskkonnas. Arendusmeeskonna juhtumine DevOps praktikate alusel.}{Web application development, scaling and securing. Working with large deployments on cloud infrastructure. Running a team in DevOps mode.}
	
}

%------------------------------------------------

\NewEntry{2008--2012}{Senior Core Library Developer, \textsc{Skype}  --- Tallinn}

\Description{\MarginText{Skype Engineering Ltd.}\ifet{Skype Core Library ehk Skype tuumiteenuste C++ teegi arhitekt ja arendaja. Tegelesin madala taseme klient-server ning P2P protokollidega, s.h. kõne ja video voogedastuse protokollidega.
		Viimased kolm kuud sellest ajast olin Microsoft Corporationi Principal Software Development Engineer.}{Architect and developer of Skype Core Library, the cross-platform C++ runtime that implements most of functionality found in Skype clients. Responsibility areas included low-level networking and P2P media and signalling transport protocols. Took part of design and implementation of  transport layer for Group Video Calling feature.
		For the last three months I was employed as Principal Software Development Engineer in Microsoft Corporation.}\newline
		\competencies{C++, Python, TCP/IP võrguprotokollid, hajus ning paralleelne programmeerimine, pehme reaalaja tarkvarasüsteemid, algoritmide ja protokollide disain}{C++, Python, IP networking, distributed and concurrent programming, semi-realtime software systems, algorithm and protocol design}
	
	
}
% \\ Reference: Bill \textsc{Lumbergh}\ \ +1 (000) 111 1111\ \ $\cdotp$\ \ \href{mailto:bill@initech.com}{bill@initech.com}}

%------------------------------------------------
\pagebreak
\NewEntry{2005--2008}{Senior Backend Developer, \textsc{Skype}  --- Tallinn}

\Description{\MarginText{Skype Engineering Ltd.}\ifet{Skype keskteenuste arhitekt ja arendaja. Tegelesin põhiliselt kõnehalduse ning kõne voogedastuse komponentidega. Põhiosa tööst seisnes suure koodimahu ning kõrgete jõudlus- ja käideldavusnõuetega C++ rakenduste loomises ning nende opereerimise toetamises.}{Architect and developer of several Skype serverside components, including the ones responsible for call signalling and media transport. Majority of the work involved writing and maintaining large C++ codebases and supporting operational staff in maintaining applications built from those codebases.}\newline
		\competencies{C++, Python, TCP/IP võrguprotokollid, hajus ning paralleelne programmeerimine, pehme reaalaja tarkvarasüsteemid, algoritmide ja protokollide disain}{C++, Python, IP networking, distributed and concurrent programming, semi-realtime software systems, algorithm and protocol design}
			
}

%------------------------------------------------

\NewEntry{1998--2005}{\ifet{Süsteemiinsener}{Computer Engineer}, \textsc{Pankade Kaardikeskus}  --- Tallinn}

\Description{\MarginText{Pankade Kaardikeskuse AS}\ifet{Erinevad ametikohustused UNIXi serveri administraatorist kaardimakseprotokollide disainimise ja standardiseerimiseni. Firma tänane nimi on Nets Estonia.}{Evolved from network manager to lead software engineer over time and got involved in nation-wide payment network redesign efforts. This company is today known as Nets Estonia.}\newline
	\competencies{UNIX/Linux, C/C++, Java, Windows, protokollide disain, andmeturve}{UNIX/Linux, C/C++, Java, Windows, protocol design, standard development, data security}
	
}

%------------------------------------------------

\NewEntry{1992--1998}{\ifet{Arvutiinsener}{Computer Technician}, \textsc{Spin TEK}  --- Tallinn}

\Description{\MarginText{Spin TEK AS}\ifet{Arvutite remont, arvutivõrkude ehitus ja hooldus}{Part-time job, consisted mostly of computer and network repair and management.}\newline
	\competencies{Windows, Linux, Novell Netware, IP ja IPX arvutivõrgud}{Windows, Linux, Novell Netware, IP and IPX networking}
}

%------------------------------------------------

%\NewEntry{Jan-Mar 2011}{Computer Technician, \textsc{Buy More} --- Burbank}

%\Description{\MarginText{Buy More}Worked in the Nerd Herd and helped to solve computer problems by asking customers to turn %their computers off and on again. \\ Reference: Big \textsc{Mike}\ \ +1 (000) 111 1111\ \ $\cdotp$\ \ %\href{mailto:mike@buymore.com}{mike@buymore.com}}

%------------------------------------------------

\vspace{0.8em} % Extra space between major sections


%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{\ifet{Publikatsioonid}{Publications}}\vspace{1em}

%\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
%\vspace{0.5em}} % Add some white space after each new entry

%\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here


\newcommand{\NewPub}[2]{\hangindent=2em\hangafter=0\noindent\raggedright{#1}\par\normalsize\vspace{0.8em}\hangindent=2em\hangafter=0\footnotesize{#2}\par\normalsize\vspace{1em}} 

\NewPub{\MarginText{\ifet{Riigi Infosüsteemi Amet}{Estonian Information System Authority}, 2021}\ifet{Krüptoalgoritmid ning nende tugi teekides ja infosüsteemides.}{Cryptographic algorithms, their lifecycle and software support.}}{\ifet{Autorid}{Authors}: Mart Oruaas, Aivo Kalu, Jaak Pruulmann-Vengerfeldt, Kristjan Krips, Jan Willemson}

\NewPub{\MarginText{Keynote paper at Baltic DB\&IS 2020}Developing requirements for the new encryption mechanisms in the Estonian eID infrastructure.}{\ifet{Autorid}{Authors}: Mart Oruaas, Jan Willemson}

\NewPub{\MarginText{Cybernetica AS, 2018}European Patent EP3529948B1 -- Composite Digital Signatures.}{\ifet{Autorid}{Authors}: Ahto Buldas, Aivo Kalu, Peeter Laud, Mart Oruaas}

\NewPub{\MarginText{ESORICS 2017}Server-Supported RSA Signatures for Mobile Devices.}{\ifet{Autorid}{Authors}: Ahto Buldas, Aivo Kalu, Peeter Laud, Mart Oruaas}


\NewPub{\MarginText{\ifet{Vabariigi Valimiskomisjon}{Estonian National Electoral Committee}, 2003}\ifet{E-hääletamise turvaanalüüs}{Security Analysis of a Proposed E-voting System}}{E-hääletamise kontseptsiooni turve: analüüs ja meetmed, EH-02-01.\\ \ifet{Autorid}{Authors}: Arne Ansper, Ahto Buldas, Mart Oruaas, Jaan Priisalu, Anto Veldre, Jan Willemson, Kaur Virunurm}



%------------------------------------------------

%\NewEntry{Sept. 2012}{Publication Title}

%\Description{\MarginText{Full Journal Name}Lorem ipsum dolor sit amet, consectetur adipiscing elit. Ut nisl tellus, sodales non pulvinar in, adipiscing sit amet purus. Suspendisse sed facilisis diam. Sed ornare sem nec justo adipiscing nec venenatis lectus commodo. Mauris non neque ligula. Pellentesque sed quam eu felis iaculis iaculis ac a leo. Suspendisse neque neque, placerat id adipiscing et, elementum eu sem.\\ Authors: John \textsc{Smith}, ~James \textsc{Smith}}

%------------------------------------------------

\vspace{0.3em} % Extra space between major sections



%----------------------------------------------------------------------------------------
%	OTHER INFORMATION
%----------------------------------------------------------------------------------------
%\pagebreak
\spacedlowsmallcaps{\ifet{Muu informatsioon}{Other Information}}\vspace{1em}

\Description{\MarginText{\ifet{Auhinnad}{Awards}}2018\ \ $\cdotp$\ \ \ifet{Aasta tegija, Cybernetica AS}{Employee of the Year of Cybernetica AS} }

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{2015\ \ $\cdotp$\ \ \ifet{Aasta üllataja, Cybernetica AS}{Amazing Newcomer award of Cybernetica AS} }

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{2005-2012\ \ $\cdotp$\ \ \ifet{Mitmed Skype sisemised auhinnad edukate projektide eest}{Multiple collegiate awards of Skype Technologies Ltd.}}


%------------------------------------------------

%\vspace{1em}

%\Description{\MarginText{Communication Skills}2010\ \ $\cdotp$\ \ Oral Presentation at the California Business Conference}

%\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

%\Description{2009\ \ $\cdotp$\ \ Poster at the Annual Business Conference in Oregon}

%------------------------------------------------

\vspace{1em}

\newlength{\langbox} % Create a new length for the length of languages to keep them equally spaced
\settowidth{\langbox}{English} % Length equals the length of "English" - if you have a longer language in your list put it here

\Description{\MarginText{\ifet{Keeleoskus}{Languages}}\parbox{\langbox}{\textsc{\ifet{Eesti}{Estonian}}}\ \ $\cdotp$\ \ \ \ifet{Emakeel}{Mothertongue}}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{\ifet{Inglise}{English}}}\ \ $\cdotp$\ \ \ \ifet{Väga hea}{Fluent in everyday and professional use}}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{\ifet{Vene}{Russian}}}\ \ $\cdotp$\ \ \ \ifet{Põhitase}{Basic}}

\vspace{1em} % Negative vertical space to counteract the vertical space between every \Description command

%------------------------------------------------

%\Description{\MarginText{\ifet{Huvid}{Interests}}\ifet{Purjetamine}{Sailing}\ \ $\cdotp$\ \ \ifet{Jooksmine}{Running}\ \ $\cdotp$\ \ \ifet{Jalgrattasõit}{Mountain biking}}

%----------------------------------------------------------------------------------------

\end{cv}

\end{document}